Local real space operators for translating Stokes Q/U to E/B maps on the sphere

### 2017-10-21 articles/draft/sections/generalizedeb.tex
added a new section on generalized operators

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Explaining the oscillations in spectra and recovering the true spectra}

@@

While translating from Stokes Q \& U parameters which form a spin-2 field to spin-0 scalars E \& B, the azimuthal part of the convolution is restricted to have the form $e^{-i2\phi}$. The only freedom is to choose the radial part of the convolution kernel.  It is possible to generalize the form of the radial kernel by introducing the following redefinition,
%
\beq
G_{QU \rightarrow EB}(\beta) = G(\beta) = \sum _{\ell=\ell_{\rm min}} ^{\ell_{\rm max}} b_{\ell}\sqrt{\frac{2 \ell+1}{4 \pi} \frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \,,\label{eq:mod_rad_forward}
\eeq
%
where $b_{\ell}$ encodes the desired changes to the radial function. This radial function now defines the modified forward operator $\bar{O}'$. Since we require the following property: $\bar{O}' \bar{O}'^{-1} = I$ to hold true, the inverse operator cannot have the same form for the radial function. Demanding $\bar{O}' \bar{O}'^{-1} = I$ to hold true it can be shown that the radial part of the inverse operator has to take up the following form,
%
\beq
G_{EB \rightarrow QU}(\beta) = G^{-1}(\beta) = \sum _{\ell=\ell_{\rm min}} ^{\ell_{\rm max}} b_{\ell}^{-1}\sqrt{\frac{2 \ell+1}{4 \pi} \frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \,,\label{eq:mod_rad_inverse}
\eeq
%
where $b_{\ell}$ is the same multipole function introduced in \eq{eq:mod_rad_forward}. Therefore for the forward and backward operators to be well behaved we are restricted in choosing multipole functions $b_{\ell}$ such that its inverse is well defined. If this constraint is overlooked, the ability to transform back and forth between the Stokes parameters and the scalar representation of the CMB polarization field is compromised. Given this general definition for the radial function $G(\beta)$, note that the radial function $R(\beta)$ is just a special case formed by making the choice $b_{\ell}=1$. Note that for this choice the inverse of the multipole function is itself $b_{\ell}^{-1} = b_{\ell}$ and therefore $G^{-1}(\beta) = G(\beta)$.

>>>>

%--------------------------------------------------------
%--------------------------------------------------------
\comment{How does the radial kernel reduce to unity on evaluating the the operator on to its inverse ? This will be important to understand how to define alternate radial functions.}
\section{Generalized operators}
The azimuthal dependence of the convolution kernels which translate the Stokes parameters Q \& U to the scalar E \& B is determined by the spin properties of the field being operated upon and the spin of the resultant fields. Hence there is no freedom in the choice of function for the azimuthal dependence of the convolution kernels. The radial part of the function however is determined by the choice of the basis functions.  It is possible to generalize these convolution kernels by choosing alternate forms for the radial functions.

We can characterize different forms of the radial kernel by introducing the following harmonic space operator,
%
\beq
\tilde{\mathcal{G}} = {\begin{bmatrix} b_{\ell}^E & 0  \\  0 & b_{\ell}^B \end{bmatrix}} \,,
\eeq
%
where the functions $b^E_{\ell}$ and $b^B_{\ell}$ represent the harmonic representation of the modified radial functions and can in the most general case be chosen to be different for E and B modes. To simplify the discussion and without loosing this generality we proceed with the assumption $b_{\ell}^E = b_{\ell}^B= b_{\ell}$. We can chose this function to be any arbitrary function and it will allow us to define some convolution operator which either translates Stokes Q \& U parameters to scalars E \& B or vice verse. Given $\tilde{\mathcal{G}}$ the modified forward and inverse convolution kernels are given by the following expressions,
%
\begin{subequations} \label{eq:gen_qu2eb}
\beqry
{\bar O}' &=& {{}_0\mathcal{Y}} *\tilde T^{-1}*\tilde{\mathcal{G}}* {{}_2\mathcal{Y}^{\dagger}} *\bar T \,,\\
{\bar O}'^{-1}&=& \bar{T}^{-1} *{{}_2\mathcal{Y}}* \tilde{\mathcal{G}}^{-1} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}
\eeqry
\end{subequations}
%
where we have used the primed notation  to distinguish these generalized operators from the default operators defined in \sec{sec:qu2eb} and \sec{sec:eb2qu}. Note that for an arbitrary choice of $\tilde{\mathcal{G}}$ only one of the operators in \eq{eq:gen_qu2eb} is well defined, since $\tilde{\mathcal{G}}^{-1}$ may be ill defined. If we require both the forward and inverse hold true, then we are constrained in choosing $\tilde{\mathcal{G}}$ such that its inverse is well defined.

@@

While translating from Stokes Q \& U parameters which form a spin-2 field to spin-0 scalars E \& B, the azimuthal part of the convolution is restricted to have the form $e^{-i2\phi}$. The only freedom is to choose the radial part of the convolution kernel.  It is possible to generalize the form of the radial kernel by introducing the following redefinition,
%
\beq
G_{QU \rightarrow EB}(\beta) = G(\beta) = \sum _{\ell=\ell_{\rm min}} ^{\ell_{\rm max}} b_{\ell}\sqrt{\frac{2 \ell+1}{4 \pi} \frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \,,\label{eq:mod_rad_forward}
\eeq
%
where $b_{\ell}$ encodes the desired changes to the radial function. This radial function now defines the modified forward operator $\bar{O}'$. Since we require the following property: $\bar{O}' \bar{O}'^{-1} = I$ to hold true, the inverse operator cannot have the same form for the radial function. Demanding $\bar{O}' \bar{O}'^{-1} = I$ to hold true it can be shown that the modified operator and its inverse is given by the following equations,
%
\begin{subequations}
\beqry
{\bar O} &=& {{}_0\mathcal{Y}} *\tilde T^{-1}*\tilde{\mathcal{G}}* {{}_2\mathcal{Y}^{\dagger}} *\bar T \,,\\
{\bar O}^{-1}&=& \bar{T}^{-1} *{{}_2\mathcal{Y}}* \tilde{\mathcal{G}}^{-1} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}
\eeqry
\end{subequations}
%
where it can be shown that the radial part of the inverse operator has to take up the following form,
%
\beq
G_{EB \rightarrow QU}(\beta) = G^{-1}(\beta) = \sum _{\ell=\ell_{\rm min}} ^{\ell_{\rm max}} b_{\ell}^{-1}\sqrt{\frac{2 \ell+1}{4 \pi} \frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \,,\label{eq:mod_rad_inverse}
\eeq
%
where $b_{\ell}$ is the same multipole function introduced in \eq{eq:mod_rad_forward}. Therefore for the forward and backward operators to be well behaved we are restricted in choosing multipole functions $b_{\ell}$ such that its inverse is well defined. If this constraint is overlooked, the ability to transform back and forth between the Stokes parameters and the scalar representation of the CMB polarization field is compromised. Given this general definition for the radial function $G(\beta)$, note that the radial function $R(\beta)$ is just a special case formed by making the choice $b_{\ell}=1$. Note that for this choice the inverse of the multipole function is itself $b_{\ell}^{-1} = b_{\ell}$ and therefore $G^{-1}(\beta) = G(\beta)$.

### 2017-10-21 articles/draft/sections/numerical_implementation.tex
added a new section on generalized operators

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Constructing E \& B maps using local convolutions}
Here we present the results of evaluating the local convolution given in \eq{eq:op_qu2eb}, to derive E \& B mode maps given maps of Stokes Q \& U. The resultant maps are depicted in \fig{fig:eb-maps-compare}. Specifically the left column depicts the reference E \& B maps derived using Healpix, the middle column depicts the E \& B mode maps derived from local convolutions restricted to $2\beta_o$ and difference between these maps is depicted in the right column. The differences between these maps are observed to be large near the polar caps, however they are significantly smaller in the band around the equator. Further note that the differences seen around the equator are dominated by large scale modes, in contrast to the polar caps where one even observes small scale fluctuations.
%
\begin{figure}[!t] 
\centering
\subfigure[E-mode Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/emap-healpix.pdf}}
\subfigure[E-mode local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/emap-2beta.pdf}}
\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/emap-diff.pdf}}
\subfigure[B-mode Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/bmap-healpix.pdf}}
\subfigure[B-mode local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/bmap-2beta.pdf}}
\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/bmap-diff.pdf}}
\caption{{\textit Left:} Reference E \& B mode maps derived using Healpix. {\textit Middle:} E \& B mode maps derived using $r_{\rm cutoff}=2\beta_o$. The color scale is saturated to that of the respective reference maps. {\textit Right:} Difference between the maps shown in the left and middle columns.}
\label{fig:eb-maps-compare}
\end{figure}
%

>>>>

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Constructing E \& B maps using local convolutions} \label{sec:local_conv_eb}
Here we present the results of evaluating the local convolution given in \eq{eq:op_qu2eb}, to derive E \& B mode maps given maps of Stokes Q \& U. The resultant maps are depicted in \fig{fig:eb-maps-compare}. Specifically the left column depicts the reference E \& B maps derived using Healpix, the middle column depicts the E \& B mode maps derived from local convolutions restricted to $2\beta_o$ and difference between these maps is depicted in the right column. The differences between these maps are observed to be large near the polar caps, however they are significantly smaller in the band around the equator. Further note that the differences seen around the equator are dominated by large scale modes, in contrast to the polar caps where one even observes small scale fluctuations.
%
\begin{figure}[!t] 
\centering
\subfigure[E-mode Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/emap-healpix.pdf}}
\subfigure[E-mode local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/emap-2beta.pdf}}
\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/emap-diff.pdf}}
\subfigure[B-mode Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/bmap-healpix.pdf}}
\subfigure[B-mode local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/bmap-2beta.pdf}}
\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/bmap-diff.pdf}}
\caption{{\textit Left:} Reference E \& B mode maps derived using Healpix. {\textit Middle:} E \& B mode maps derived using $r_{\rm cutoff}=2\beta_o$. The color scale is saturated to that of the respective reference maps. {\textit Right:} Difference between the maps shown in the left and middle columns.}
\label{fig:eb-maps-compare}
\end{figure}
%

### 2017-10-21 articles/draft/sections/real_space_formalism.tex
added a new section on generalized operators

\rfedit{The azimuthal operations do not depend on the choice of basis functions, and can be argued as a requirement for constructing spin-0 fields by operating on spin-2 fields. The radial kernel however is determined by the choice of the basis functions. Motivated by this observation, one can now think of working with alternate basis functions which have different radial fall off.} \comment{This is generally true for all the local kernels. So shift this line to the section where we explore different radial functions.}
%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Evaluating Stokes parameters Q \& U fields from E \& B fields}\label{sec:eb2qu}
The real space operator which translates E \& B fields to Stokes parameters Q \& U is derived using a similar procedure. The inverse operator is given by the following expression,
%
\beqry
\bar{P} &=& \bar{T}^{-1} *{{}_2\mathcal{Y}} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} *{{}_2\mathcal{Y}} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}\bar{S}   \\
&=&  \bar O^{-1} *\bar{S}
\eeqry
%
We do not provide the explicit calculations here, since the derivation is nearly identical to that discussed in the previous section. The inverse operator is given by the following expression,
%
\beq
{\bar O}^{-1}=-\bmat \mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,.
\eeq
%
%where all the symbols have the same meaning as discussed in \sec{sec:qu2eb}.
Note that the kernel is different by a mere change in sign on the off-diagonals of the block matrix as compared to \eq{eq:op_qu2eb}.
We can evaluate the Stokes Q \& U parameters from the scalar E \& B  fields by evaluating the following expression,
%
\beq
\bmat Q_i \\ U_i  \emat=-\Delta \Omega\sum_{j=1}^{N_{\rm pix}}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat E_j \\ B_j  \emat \,,
\eeq
%
where all the symbols have their usual meaning. The above equation can again be expressed more concisely as follows,
%
\begin{subequations} \label{eq:eb2qu_simple}
\beqry 
[Q + iU](\hat{n}_0) &=& - \Delta \Omega \sum_{j=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}} P_{\ell}^{2}(\beta_{0j}) \right)  \mathbf{\Bigg( e^{i2 \alpha_{0j}}   [E+iB](\hat{n}_j) \Bigg)} \,, \label{eq:eb2qu_physical}\\
{}_{+2}X(\hat{n}_0) &=& - \left( \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2} \right]  \circ [E+iB] \right)\,, 
\eeqry
\end{subequations}
%
which is to be interpreted in the same manner as \eq{eq:qu2eb_simple}. Note that the only change in the convolution kernel as compared to that in \eq{eq:op_qu2eb} is that the signs of the off-diagonal block matrices are reversed. Alternatively, the $Y_{\ell 2}$ functions are not conjugated. This can again be simply understood as constructing a spin-2 field by taking a product of a spin-0 field: $[E +iB]$ with a spin $+2$ field: $\exp(+i2\alpha)$. The radial dependence of the operator ${\bar O}^{-1}$  is identical to the that of ${\bar O}$ as one may have expected. In this case all the coordinate dependence in encoded in the function $\exp(+i2\alpha)$, which is ill-defined at the poles ($\beta \rightarrow 0,\pi$) and hence the radial functions have to vanish at these locations, which is the case for the same reasons discussed previously.

\comment{How does the radial kernel reduce to unity on evaluating the the operator on to its inverse ? This will be important to understand how to define alternate radial functions.}

@@

&=& 0.5 \Bigg\lbrace I^* \circ {}_{+2}X\pm D \circ {}_{+2}X^* \Bigg\rbrace \,, \label{eq:qu2equbqu_convolution}

@@

It is easy to show that the operator $D$ is a complex but symmetric matrix and that the operator $I$ is Hermitian. The function $I$ is a band limited version of the delta function ($\lim_{\ell \rightarrow \infty} I = \delta(\hat{n}_i - \hat{n}_j)$), when interpreted as a matrix operator forms a band limited version of the identity matrix. Though its non-local ($I \neq 0 $ when $\hat{n}_i \neq \hat{n}_j$) owing to the band limit, for all practical purposes the operator $I$ acts like an identity operator as is confirmed by the following identities it satisfies: (i) $I*I=I$ ; (ii) $D*I=D$. Also $D^*$ is the inverse of $D$ in this band limited sense: $D^**D=I$. Using these properties of the operators $I$ and $D$, one can verify that the real space operators satisfy the following identities,
%
\begin{subequations}
\beqry
\bar O_E * \bar O_E &=& \bar O_E ~~;~~ \bar O_B * \bar O_B = \bar O_B \,, \\
\bar O_E*\bar O_B &=& 0 \,,\\
\bar O_E + \bar O_B &=& I \,,
\eeqry
\end{subequations}
%
which are the real space analogues of \eq{eq:har_op_prop}. While testing the above stated identities one encounters terms like $D*I^*,I^**I \textrm{ and }  I*I^*$ which cannot be simply interpreted, but they always occur in pairs with opposite signs, hence exactly canceling each other. \revisit{Note that unlike in the harmonic case, the sum of the operators is not exactly an identity matrix. \comment{Isn't it possible to do some real space operations which doesn't care for the band limit but still returns the required decomposition into the respective scalar modes ?} This indicates the loss of information occurred from the original data due to making this transformations with some assumed band limit. If one forces the sum of the operators to be exactly an identity operator, then one compromises on the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators.}

>>>>

\rfedit{The azimuthal operations do not depend on the choice of basis functions, and can be argued as a requirement for constructing spin-0 fields by operating on spin-2 fields. The radial kernel however is determined by the choice of the basis functions. Motivated by this observation, one can now think of working with alternate basis functions which have different radial fall off.} \comment{This is generally true for all the local kernels. So shift this line to the section where we explore different radial functions.}
\subsection{Evaluating Stokes parameters Q \& U fields from E \& B fields}\label{sec:eb2qu}
The real space operator which translates E \& B fields to Stokes parameters Q \& U is derived using a similar procedure. The inverse operator is given by the following expression,
\bar{P} &=& \bar{T}^{-1} *{{}_2\mathcal{Y}} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} *{{}_2\mathcal{Y}} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}\bar{S}   \\
&=&  \bar O^{-1} *\bar{S}
We do not provide the explicit calculations here, since the derivation is nearly identical to that discussed in the previous section. The inverse operator is given by the following expression,
{\bar O}^{-1}=-\bmat \mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,.
%where all the symbols have the same meaning as discussed in \sec{sec:qu2eb}.
Note that the kernel is different by a mere change in sign on the off-diagonals of the block matrix as compared to \eq{eq:op_qu2eb}.
We can evaluate the Stokes Q \& U parameters from the scalar E \& B  fields by evaluating the following expression,
\bmat Q_i \\ U_i  \emat=-\Delta \Omega\sum_{j=1}^{N_{\rm pix}}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat E_j \\ B_j  \emat \,,
where all the symbols have their usual meaning. The above equation can again be expressed more concisely as follows,
\begin{subequations} \label{eq:eb2qu_simple}
[Q + iU](\hat{n}_0) &=& - \Delta \Omega \sum_{j=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}} P_{\ell}^{2}(\beta_{0j}) \right)  \mathbf{\Bigg( e^{i2 \alpha_{0j}}   [E+iB](\hat{n}_j) \Bigg)} \,, \label{eq:eb2qu_physical}\\
{}_{+2}X(\hat{n}_0) &=& - \left( \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2} \right]  \circ [E+iB] \right)\,, 
which is to be interpreted in the same manner as \eq{eq:qu2eb_simple}. Note that the only change in the convolution kernel as compared to that in \eq{eq:op_qu2eb} is that the signs of the off-diagonal block matrices are reversed. Alternatively, the $Y_{\ell 2}$ functions are not conjugated. This can again be simply understood as constructing a spin-2 field by taking a product of a spin-0 field: $[E +iB]$ with a spin $+2$ field: $\exp(+i2\alpha)$. The radial dependence of the operator ${\bar O}^{-1}$  is identical to the that of ${\bar O}$ as one may have expected. In this case all the coordinate dependence in encoded in the function $\exp(+i2\alpha)$, which is ill-defined at the poles ($\beta \rightarrow 0,\pi$) and hence the radial functions have to vanish at these locations, which is the case for the same reasons discussed previously.

@@

&=& 0.5 \Bigg\lbrace \mathcal{I}^* \circ {}_{+2}X\pm \mathcal{D} \circ {}_{+2}X^* \Bigg\rbrace \,, \label{eq:qu2equbqu_convolution}

@@

It is easy to show that the operator $\mathcal{D}$ is a complex but symmetric matrix and that the operator $\mathcal{I}$ is Hermitian. The function $I$ is a band limited version of the delta function ($\lim_{\ell \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$), when interpreted as a matrix operator forms a band limited version of the identity matrix. Though its non-local ($\mathcal{I} \neq 0 $ when $\hat{n}_i \neq \hat{n}_j$) owing to the band limit, for all practical purposes the operator $\mathcal{I}$ acts like an identity operator as is confirmed by the following identities it satisfies: (i) $\mathcal{I}*\mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D}*\mathcal{I}=\mathcal{D}$. Also $\mathcal{D}^*$ is the inverse of $\mathcal{D}$ in this band limited sense: $\mathcal{D}^**\mathcal{D}=I$. Using these properties of the operators $\mathcal{I}$ and $\mathcal{D}$, one can verify that the real space operators satisfy the following identities,
%
\begin{subequations}
\beqry
\bar O_E * \bar O_E &=& \bar O_E ~~;~~ \bar O_B * \bar O_B = \bar O_B \,, \\
\bar O_E*\bar O_B &=& 0 \,,\\
\bar O_E + \bar O_B &=& \mathcal{I} \,,
\eeqry
\end{subequations}
%
which are the real space analogues of \eq{eq:har_op_prop}. While testing the above stated identities one encounters terms like $\mathcal{D}*\mathcal{I}^*,\mathcal{I}^**\mathcal{I} \textrm{ and }  \mathcal{I}*\mathcal{I}^*$ which cannot be simply interpreted, but they always occur in pairs with opposite signs, hence exactly canceling each other. \revisit{Note that unlike in the harmonic case, the sum of the operators is not exactly an identity matrix. \comment{Isn't it possible to do some real space operations which doesn't care for the band limit but still returns the required decomposition into the respective scalar modes ?} This indicates the loss of information occurred from the original data due to making this transformations with some assumed band limit. If one forces the sum of the operators to be exactly an identity operator, then one compromises on the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators.}
